---
title: "Lab-01-Becerra"
author: "Cristian Becerra"
date: "1/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

## Create a new game


```{r}
create_game <- function( )
{

    a.game <- sample( x=c("goat","goat","car"), size=3, replace=F )
 
    return( a.game )
} 
```

## Test of Function:

```{r}

# try three times to see randomization 
create_game() 

```

## Contest selects a door

```{r}

select_door <- function( )
{

  doors <- c(1,2,3) 
  a.pick <- sample( x=doors, size = 1)
  return( a.pick )  # number between 1 and 3

}

```

## Test door selection:

```{r}

# test the function
select_door()

```

## Host opens goat door

```{r}

open_goat_door <- function( game, a.pick )
{

#subset doors to exclude door already picked by contestant
  game2 <- if (a.pick == 1) {
    doors3 <- c(2,3)
  } else if (a.pick == 2) {
    doors3 <- c(1,3)
  } else if (a.pick == 3) {
    doors3 <- c(1,2)
  }
  
#if door has car then show contest other door. Otherwise sample randonly from the two remaining doors if contestant correctly chose car first
opened.door <-  if ( game[game2[1]] == "car") {
 doors2 <- game2[2]
  h.pick <- doors2
 } else if ( game[game2[2]] == "car") {
 doors2 <- game2[1] 
  h.pick <- doors2
 } else {
 doors2 <- game2 
  h.pick <- sample( x=doors2, size = 1)
 }
   
   return( opened.door ) # number between 1 and 3

}
```

```{r}

this.game <- create_game()

this.game

my.initial.pick <- select_door()

my.initial.pick

open_goat_door( this.game, my.initial.pick )

```

## Change Doors

```{r}
change_door <- function( stay=T, opened.door, a.pick )
{
  #opened.door <- 1
  #a.pick <- 2
  
  
  
  final.pick <- if(stay == T) {
    a.pick
  } else if(opened.door==1 & a.pick==2){
    3
  } else if (opened.door==1 & a.pick==3){
    2
  } else if (opened.door==2 & a.pick == 3){
    1
  } else if (a.pick==1 & opened.door==2){
    3
  } else if (a.pick==1 & opened.door==3){
    2
  } else if (a.pick==2 & opened.door==3){
    1
  }
  #final.pick
   return( final.pick )  # number between 1 and 3

}
```

```{r}
# test it

opened.door <- open_goat_door( this.game, my.initial.pick )

change_door( stay=T, opened.door=opened.door, a.pick=my.initial.pick )
change_door( stay=F, opened.door=opened.door, a.pick=my.initial.pick )

my.final.pick <- change_door( stay=F, opened.door=opened.door, a.pick=my.initial.pick )

this.game
my.initial.pick
my.final.pick 

```

## Determine if contestant won

```{r}

determine_winner <- function( final.pick, game )
{

   if( this.game[final.pick] == "car" )
   {
      return( "WIN" )
   }
   if( this.game[final.pick] == "goat" )
   {
      return( "LOSE" )
   }

}

```

```{r}

# test code

this.game
my.initial.pick

my.final.pick <- change_door( stay=T, opened.door=opened.door, a.pick=my.initial.pick )
determine_winner( final.pick=my.final.pick, game=this.game )

my.final.pick <- change_door( stay=F, opened.door=opened.door, a.pick=my.initial.pick )
determine_winner( final.pick=my.final.pick, game=this.game )

```

## Test the Game

```{r}

# your game "recipe" 
this.game <- create_game()
my.initial.pick <- select_door()
opened.goat.door <- open_goat_door( this.game, my.initial.pick )
# save results for both strategies for the game
my.final.pick.stay <- change_door( stay=T, opened.door=opened.goat.door, a.pick=my.initial.pick )
my.final.pick.switch <- change_door( stay=F, opened.door=opened.goat.door, a.pick=my.initial.pick )

# print game details and if you won

# if you stayed:
paste0( "GAME SETUP" )
this.game
paste0( "My initial selection: ", my.initial.pick )
paste0( "The opened goat door: ", opened.goat.door )
paste0( "My final selection: ", my.final.pick.stay )
paste0( "GAME OUTCOME:" )
determine_winner( final.pick=my.final.pick.stay, game=this.game )

# if you switched:
paste0( "GAME SETUP" )
this.game
paste0( "My initial selection: ", my.initial.pick )
paste0( "The opened goat door: ", opened.goat.door )
paste0( "My final selection: ", my.final.pick.switch )
paste0( "GAME OUTCOME:" )
determine_winner( final.pick=my.final.pick.switch, game=this.game )

```

## Challenge Questions

PART 01:
Let’s change the rules a little to make outcomes more interesting. Create a board with 5 doors and 2 cars. After the contestant makes an initial selection the host will open one car door and one goat door. If the contestand decides to switch they then have to select from the two remaining doors.
How does this new board change the pay-off from the game? Is switching still the best strategy?

**Answer:** Switching is still the best strategy. Increasing the numbers of doors and cars creates two scenarios where staying will win the car, this reduces the odds of switching being the best option but switching will still be the right option 60% of the time. 

PART 02:
We are building functions to play a game in a static world. There are always three doors, one car, and two goats.

What happens if we are in a dynamic world? The game can have three or more doors (in a game with two doors there would be no switching so there is no strategy to study). And we can also have one or more cars up to N-2 (N being the number of doors, there always need to be at least two goats so that the host can open a goat door, even if the contestant selected a goat in the first round).
How would you change the code to model this new world?

**Answer:** I would create input variables that allow the user to create the parameters for the create game function. The user would be able to define how many goats/cars exists within a total number of doors and the function would sample correctly. The rest of the simulation would also have to be reactive to the initial input. This starts to get more complicated and I would likely have to restructure all static code, but it would need to know how many cars/goats exists and correctly detect a door to open with the goat. An idea is to create dataframes where a filter is applied so the selection of which door to open is capable of happening no matter the number of doors or initial selection, then turn that dataframe back into a list if needed. Rather than creating if statements that are applied to a list of a certain size.

